GVN-Hoist: Hoisting Computations from Branches

### 2016-08-10 hoist.tex
dfs depth

Essentially,
abs(DFSIn(I1) - DFSIn(I2)) < abs(DFSIn(I1) - DFSIn(I3))
=> bbDist(I1, nearest-common-dom(I1, I2)) <= bbDist(I1, nearest-common-dom(I1, I3))

>>>>

\begin{verbatim}
Essentially if,
DFS-I1I2 = abs(DFSIn(I1) - DFSIn(I2))
DFS-I1I3 = abs(DFSIn(I1) - DFSIn(I3))
BBDistI1I2 = bbDist(I1, nearest-common-dom(I1, I2))
BBDistI1I3 = bbDist(I1, nearest-common-dom(I1, I3))

Then,
DFS-I1I2 < DFS-I1I3 => BBDistI1I2 <= BBDistI1I3
\end{verbatim}
